### 2021-05-26 sections/appendix/descrete_event_simulation/main.tex
Write appendix chapter for DES model

% TODO: Include details of DES

>>>>

For the purposes of this study, a discrete event simulation (DES) model was
constructed to support the Markov chain version described in 
section~\ref{sec:queueing_model}.
The queueing model was built in python using the Ciw 
library~\cite{ciwpython}.

The constructed model simulates a queueing system with two waiting spaces and 
two types of individuals. 
The expected behaviour of the nodes in Ciw have been modified such that 
individuals moving from waiting zone 2 into waiting zone 1 may remain blocked 
if there are more than \(T\) individuals in waiting zone 1.

The same performance measures described in sections 
\ref{sec:waiting_time}, \ref{sec:blocking_time} and 
\ref{sec:proportion_within_target} can also be calculated using the DES model.
The simulation can be ran a number of times to eliminate stochasticity and the
outcomes of the two methods can be directly comparable.

% TODO: Include the queueing model diagram here?
% TODO: Include python code here?

### 2021-05-26 sections/queueing_model/blocking_time/main.tex
Write appendix chapter for DES model

\subsubsection{Blocking time}

@@

Figure \ref{fig:markov_vs_des_blocking_time_comparison} illustrates a comparison 
between the formulas that arise from the Markov chain model and the equivalent 
values of the blocking time extracted from discrete event simulation.
The blocking time is calculated using both methods for a range of values of
\(\lambda_2\)

>>>>

\subsection{Blocking time}\label{sec:blocking_time}

@@

\subsubsection{Example}
Figure \ref{fig:markov_vs_des_blocking_time_comparison} illustrates a comparison 
between the formulas that arise from the Markov chain model and the equivalent 
values of the blocking time extracted from discrete event simulation
(appendix~\ref{sec:appendix_des}).
The blocking time is calculated using both methods for a range of values of
\(\lambda_2\)

### 2021-05-26 sections/queueing_model/proportion_within_target/main.tex
Write appendix chapter for DES model

\subsection{Proportion of individuals within target}

@@

\subsubsection{Example}
Figures \ref{fig:markov_vs_des_proportion_comparison_1},
\ref{fig:markov_vs_des_proportion_comparison_2} and 
\ref{fig:markov_vs_des_proportion_comparison_overall} show a comparison of the
mean proportion of individuals within target when using Markov chains and 
discrete event simulation.
The simulation was ran 100 times and the recorded proportions at each iteration 
is used to populate the violin plots.

>>>>

\subsection{Proportion of individuals within target}\label{sec:proportion_within_target}

@@

\subsubsection{Example}
Figures \ref{fig:markov_vs_des_proportion_comparison_1},
\ref{fig:markov_vs_des_proportion_comparison_2} and 
\ref{fig:markov_vs_des_proportion_comparison_overall} show a comparison of the
mean proportion of individuals within target when using Markov chains and 
discrete event simulation (appendix~\ref{sec:appendix_des}).
The simulation was ran 100 times and the recorded proportions at each iteration 
is used to populate the violin plots.
